\Huge \bf Implementation of a quadrotor UAV

### 2012-07-15 latex/paper/paper.tex
descrip a las figuras, achico imag

\begin{abstract}
%\boldmath
This paper describes the design and integration of a control system that allows the autonomous flight of a radio controlled commercial quadcopter. A mathematical model for the quadcopter is developed, its parameters determined from the characterization of the unit. An external intelligence is integrated to play the rol of the flight controller. A 9 degrees of freedom Inertial Measurement Unit (IMU) equipped with a barometer is calibrated and added to the platform. Data from the IMU is combined with the information provided by a GPS within a Extended Kalman Filter (EKF) to obtain a reliable estimation of the state variables every 10ms. The control actions are obtained from a proportional-integral controller based on the LQR algorithm. For windless environments, a stable platform is achieved.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the conference you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals/conferences frown on
% math in the abstract anyway.

@@

The platform is based on a commercial quadcopter, the frame and the motor control system were preserved, but the IMU and intelligence were replaced by the flight controller that was developed. An ARM-Cortex-A8 processor running Linux performs the computations requiered to convert raw IMU data and combine it using an EKF, overcoming the noise generated by the vibrations of the motors, and providing a reliable estimation of the state variables. Once the current state is known, the LQR algorithm\cite{bib:lqrnotes}\cite{bib:lqr-discreto} is used to derive control actions required to bring the system to the desired setpoint.

@@

\begin{figure}
	\centering
	\includegraphics[width=1\columnwidth]{./pics_paper/quad_coord.jpg}
	\caption{Model of a quadcopter - Intertial reference (blue), Non-Inertial reference (red)}
	\label{fig:quad}
\end{figure}

@@

The equations that govern the dynamics of a quadcopter are presented in equation \ref{eq:modelo}. The reference frames used are shown in figure \ref{}.

@@

%TODO pasar figura a ingl\'e
\begin{figure}
	\centering
	\includegraphics[width=1\columnwidth]{../pics_kalman/diagrama_kalman_2.png}
	\caption{}
	\label{fig:diagrama_kalman}
\end{figure}

>>>>

\begin{abstract}
%\boldmath
This paper describes the design and integration of a control system that allows the autonomous flight of a radio controlled commercial quadcopter. A mathematical model for the quadcopter is developed, its parameters determined from the characterization of the unit. An external intelligence is integrated to play the rol of the flight controller. A 9 degrees of freedom Inertial Measurement Unit (IMU) equipped with a barometer is calibrated and added to the platform. Data from the IMU is combined with the information provided by a GPS within a Extended Kalman Filter (EKF) to obtain a reliable estimation of the state variables. The control actions are obtained from a proportional-integral controller based on the LQR algorithm. For windless environments, a stable platform is achieved.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the conference you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals/conferences frown on
% math in the abstract anyway.

@@

The platform is based on a commercial quadcopter, the frame and the motor control system were preserved, but the IMU and intelligence were replaced by the flight controller that was developed. A BeagleBoard running Linux performs the computations requiered to convert raw data received from the IMU and combine it using an EKF, overcoming the problems inherent to each sensor and the noise generated by the vibrations of the motors, and providing a reliable estimation of the state vector. Once the current state is known, the LQR algorithm\cite{bib:lqrnotes}\cite{bib:lqr-discreto} is used to derive control actions required to bring the system to the desired setpoint.

@@

\begin{figure}
	\centering
	\includegraphics[width=.7\columnwidth]{./pics_paper/quad_coord.jpg}
	\caption{\textbf{Model of the quadcopter -} Intertial reference frame in blue, non-inertial reference frame in red. Cyan looped arrows indicate the direction of rotation of each motor. The semicircle and the two yellow spheres indicate the front of the unit.}
%        \vspace{-30pt}
	\label{fig:quad}
\end{figure}

@@

The equations that govern the dynamics of a quadcopter are presented in equation \ref{eq:modelo}. The reference frames used are shown in figure \ref{fig:quad}.

@@

%TODO pasar figura a ingl\'e
\begin{figure}
	\centering
	\includegraphics[width=1\columnwidth]{../pics_kalman/diagrama_kalman_2.png}
	\caption{\textbf{EKF - } Outline of how sensor data is combined to estimate the state variables.}
	\label{fig:diagrama_kalman}
\end{figure}
